How explicit is the Explicit Formula?

### 2013-01-05 talk.tex
Fix a few typos.

\begin{frame}
 \vskip40pt {\Large  
 $$\Delta_E(X) =$$  \vskip20pt $$ \#\{p \ {\rm such\ that\ } |E({\bf F}_p| > p+1\}$$ \vskip10pt \centerline{minus} \vskip10pt  $$ \#\{p \ {\rm such\ that\ } |E({\bf F}_p| < p+1\}?$$}  \end{frame}

\begin{frame}
 \vskip40pt {\Large  Equivalently, putting:\begin{itemize} \item $\gamma_E(p)=0$ if $p$ is a bad or supersingular prime for $E$ and\vskip20pt \item i$\gamma_E(p)= -1$ if $E$ has more than $p+1$  ${\bf F}_p$-rational points, and \vskip20pt \item $\gamma_E(p) = +1$ if less.\end{itemize}}\end{frame}\begin{frame}\vskip20pt
{\Large \vskip40pt 
 So:\vskip20pt
   $$\Delta_E(X): =\sum_{p\le X}\gamma_E(p).$$

>>>>

\begin{frame}
 \vskip40pt {\Large  
 $$\Delta_E(X) =$$  \vskip20pt $$ \#\{p \ {\rm such\ that\ } |E({\bf F}_p)| > p+1\}$$ \vskip10pt \centerline{minus} \vskip10pt  $$ \#\{p \ {\rm such\ that\ } |E({\bf F}_p)| < p+1\}?$$}  \end{frame}

\begin{frame}
 \vskip40pt {\Large  Equivalently, putting:\begin{itemize} \item $\gamma_E(p)=0$ if $p$ is a bad or supersingular prime for $E$ and\vskip20pt \item $\gamma_E(p)= -1$ if $E$ has more than $p+1$  ${\bf F}_p$-rational points, and \vskip20pt \item $\gamma_E(p) = +1$ if less.\end{itemize}}\end{frame}\begin{frame}\vskip20pt
{\Large \vskip40pt 
 So:\vskip20pt
   $$\Delta_E(X): =\sum_{p\le X}\gamma_E(p).$$
